A Gentle Introduction and Application of Feature-Based Clustering with Psychological Time Series

### 2023-02-23 manuscript.tex
:construction: paragraph str and order

Thus, while the final selection of features should always be driven by the research questions and field-specific conventions, for our illustration we chose six features that relate to common psychological research questions and recent works within the field: (1) central tendency, (2) variability, (3) instability, (4) self-similarity, (5) linear trend, and (6) nonlinearity. We offer a short introduction of each of these six features below as a practical starting point for researchers and practitioners interested in feature-based clustering of psychological time series data. An overview of the proposed features, their substantive interpretations, and mathematical operationalizations is also available in \tblref{tab:esmFeatures}.

It is important to reiterate that the six selected time-series features are in no way exhaustive or imperative. Both using a more data-driven approach to features or selecting other aspects to summarize the time series are legitimate options \citep[e.g., see][]{heylen2016}. The list seeks to offer a practical toolbox of features that are common and meaningful to psychological research questions and -practice but are also easy to extract and summarize a broad range of developments without asserting strict assumptions (see \tblref{tab:esmFeatures} for an overview).

@@

>>>>

Thus, while the final selection of features should always be driven by the research questions and field-specific conventions, for our illustration we chose six features that relate to common psychological research questions and recent works within the field: (1) central tendency, (2) variability, (3) instability, (4) self-similarity, (5) linear trend, and (6) nonlinearity. An overview of the selected features, their substantive interpretations, and mathematical operationalizations is also available in \tblref{tab:esmFeatures}. We offer a short introduction of each of these six features below as a practical starting point for researchers and practitioners interested in feature-based clustering of psychological time series data. We provide additional background on the theoretical relevance of the selected features in \appref{app:FeatureBackground}.

@@

It is important to reiterate that the six selected time-series features are in no way exhaustive or imperative. Both using a more data-driven approach to the selection of features or selecting entirely different aspects to summarize the time series are legitimate options \citep[e.g., see][]{heylen2016}. Our choice seeks to offer a practical toolbox of features that are common and meaningful to psychological research questions and -practice but are also easy to extract and summarize a broad range of developments without asserting strict assumptions.
